Quantum Interval-Valued Probability: Measurement and Probability

### 2017-11-28 prop_iop.tex
prop_iop.tex \DeclareUnicodeCharacter{00A0}{~} Add to eliminate an error...
prop_iop.tex \subsection{Expectation Values for QIVPMs} Cleaning up...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\usepackage{mmap}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

Before discussing QIVPMs, we first review various notations brought
forward from conventional quantum theory. Assume that a physical system
is represented by a density matrix~$\rho$, and that we wish to measure
a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by~\cite{Griffiths1994,FraleighBeauregard1995,544199,FriedbergInselSpence2002,Jaeger2007}
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
\end{equation}
where the positive and negative eigenvalues are ordered from the smallest
to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}<\ldots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\ldots<\lambda_{N^{+}}^{+}\,,
\end{equation}
and $P_{i}$ is the projector onto the eigenspace of each distinct
eigenvalue~$\lambda_{i}$. This spectral decomposition might be different
from the one people used to~.

Since $\lambda_{i}$ are distinct, $N$ may be less than $d$. Although
we requires the eigenvalues in equation~(\ref{eq:spectrum-decomposition-distinct})
to be distinct, we will consider the other type of spectral decomposition,
especially $\mathbf{O}=\sum_{k=1}^{d}\lambda_{k}\proj{k}$ in lemma~\ref{lemma:observable2random-variable}
later. Then, the Born rule of CQT tells us that the expectation value
of the observable~$\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition

Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
\end{equation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\DeclareUnicodeCharacter{00A0}{~}
\usepackage{mmap}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

Before discussing QIVPMs, we first review various notations brought
forward from conventional quantum theory. Assume that a physical system
is represented by a density matrix~$\rho$, and that we wish to measure
a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by~\cite{Griffiths1994,FraleighBeauregard1995,544199,FriedbergInselSpence2002,Jaeger2007}
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
\end{equation}
where the positive and negative eigenvalues are ordered from the smallest
to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}<\ldots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\ldots<\lambda_{N^{+}}^{+}\,,
\end{equation}
and $P_{i}$ is the projector onto the eigenspace of each distinct
eigenvalue~$\lambda_{i}$. Compare to equation~(\ref{eq:spectrum-decomposition-distinct}),
the spectral decomposition of $\mathbf{O}$ may be represented in
term of outer product as $\mathbf{O}=\sum_{k=1}^{d}\lambda_{k}\proj{k}$
which would be used in lemma~\ref{lemma:observable2random-variable}
later. Disregard the representation of the spectral decomposition,
it can be used to defined the expectation value of the observable~$\mathbf{O}$
as~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\ .\label{eq:quantum-expectation}
\end{equation}

Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$. Similar to the classical Choquet integral
in definition~\ref{def:Choquet}, we can let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$
and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $,
and define the expectation value of $\mathbf{O}$ with respect to
$\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
\end{equation}
